Checklist

### 2019-04-26 presentations/2019-04-27_shutdown/checklist.tex
[presentation/2019-04-27_shutdown] WIP: checklists

\documentclass[10pt,fleqn,twocolumn]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{esint}
\usepackage{bbm}
\usepackage{amscd}
\usepackage{picinpar}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{tikz-3dplot}
\usepackage{indentfirst}
\usepackage{wrapfig}
\usepackage{units}
\usepackage{textcomp}
\usepackage[utf8x]{inputenc}
% \usepackage{feyn}
\usepackage{feynmp}
\usepackage{xkeyval}
\usepackage{xargs}
\usepackage{verbatim}
\usepackage{pgfplots}
\usepackage{hyperref}
\usetikzlibrary{
  arrows,
  calc,
  decorations.pathmorphing,
  decorations.pathreplacing,
  decorations.markings,
  fadings,
  positioning,
  shapes
}

@@

\parindent=0pt
\title{Checklist}
\date{August 2nd, 2017}
\begin{document}

\Person{Yichao}{
  Equipments and power supplies are mostly located around the laser table on the library side.\\
  Check Lee's part after everything are off.
}
\subsection{Equipments}
\DevDef{Thorlabs temperature controller for Na Raman doubler}{
  \textbf{1st level above Na Raman and D2 seed lasers}\\
  Record temperature settings\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox Check temperature setting
  \item\OnBox Turn on
  \end{itemize}
}
\DevDef{Timebase driver for Na Raman and Na D2 (x2)}{
  \textbf{1st level above Na Raman and D2 seed lasers}\\
  Record current and T1 settings\\

  \begin{tabular}{|c|c|}
    \hline
    Raman Current&\hphantom{\hspace{3.5cm}}\\\hline
    Raman T1&\\\hline
    MOT Current&\hphantom{\hspace{3.5cm}}\\\hline
    MOT T1&\\\hline
  \end{tabular}\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox Turn on
  \item\OnBox Set current/temperature.
  \item\OnBox Enable T1 survo
  \item\OnBox Turn on current
  \end{itemize}
}
\DevDef{Oscilloscope for Na D2 lock}{
  \textbf{1st level above Na Raman amplifier}
  \begin{itemize}
  \item\OffBox Unplug from wall
  \end{itemize}
}
\DevDef{MPB Raman amplifier}{
  \textbf{1st level above Na MOT beam path}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Power off
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into wall
  \item\OnBox Power on
  \end{itemize}
}
\DevDef{Homebuilt lockbox for Na D2}{
  \textbf{1st level above Na seed}\\
  \textbf{Turn on-off together with the adjustable high voltage power supply above}\\
  Record high voltage power supply output

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unlock
  \item\OffBox Turn down the voltage of the high voltage power supply to 0
  \item\OffBox Unplug high voltage power on lockbox (zip tie)
  \item\OffBox Unplug 15V from lockbox (zip tie)
  \item\OffBox Turn off high voltage power supply
  \item\OffBox Unplug high voltage power supply from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug high voltage power supply into the wall
  \item\OnBox Turn on high voltage power supply (make sure the output is 0)
  \item\OnBox Plug in 15V to lockbox
  \item\OnBox Plug in high voltage to lockbox
  \item\OnBox Turn up the voltage of the high voltage power supply
  \item\OnBox Check HV output
  \end{itemize}
}
\DevDef{SRS shutter driver for Na}{
  \textbf{1st level above Na D2 beam path, below Variac}\\
  Switch off/on with the switch on the back.
}
\DevDef{Variac for Na cell}{
  \textbf{Above Na D2 beam path}\\
  Record temperature and voltage settings\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn voltage to 0
  \item\OffBox Switch off
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into wall
  \item\OnBox Switch on
  \item\OnBox Turn the voltage up \textbf{SLOWLY} and monitor the temperature at the same time.
  \end{itemize}
}
\DevDef{Homebuilt lockbox for Na D1}{
  \textbf{1st level above Na D2 beam path}\\
  \textbf{Turn on-off together with the fixed high voltage power supply above}\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unlock
  \item\OffBox Unplug high voltage power on lockbox (zip tie)
  \item\OffBox Unplug 15V from lockbox (zip tie)
  \item\OffBox Unplug high voltage power supply from walls
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug high voltage power supply into the wall
  \item\OnBox Plug in 15V to lockbox
  \item\OnBox Plug in high voltage to lockbox
  \item\OnBox Check HV output
  \end{itemize}
}
\DevDef{Thorlabs temperature controller for Na D1 doubler}{
  \textbf{1st level above Na D1}\\
  Record temperature settings\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox Check temperature setting
  \item\OnBox Turn on
  \end{itemize}
}
\DevDef{Thorlabs temperature controller for Na D1 seed}{
  \textbf{1st level above Na D1 seed}\\
  Record temperature settings\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox Check temperature setting
  \item\OnBox Turn on
  \end{itemize}
}
\DevDef{Thorlabs current controller for Na D1 seed}{
  \textbf{1st level above Na D1 seed}\\
  Record current settings\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox Check current setting
  \item\OnBox Turn on
  \end{itemize}
}
\subsection{Power supplies}
\DevDef{Benchtop power supply}{
  \textbf{2nd level above Na Variac}\\
  Record voltage/current values:\\

>>>>

\documentclass[10pt,fleqn,twocolumn]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{esint}
\usepackage{bbm}
\usepackage{amscd}
\usepackage{picinpar}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{tikz-3dplot}
\usepackage{indentfirst}
\usepackage{wrapfig}
\usepackage{units}
\usepackage{textcomp}
\usepackage[utf8x]{inputenc}
% \usepackage{feyn}
\usepackage{feynmp}
\usepackage{xkeyval}
\usepackage{xargs}
\usepackage{verbatim}
\usepackage{pgfplots}
\usepackage{hyperref}
\usepackage{longtable}

\usetikzlibrary{
  arrows,
  calc,
  decorations.pathmorphing,
  decorations.pathreplacing,
  decorations.markings,
  fadings,
  positioning,
  shapes
}

@@

\parindent=0pt
\title{Checklist}
\date{April 27th, 2019}
\begin{document}

\onecolumn
\Person{Yichao}{
  Equipments and power supplies are mostly located around the laser table facing the wall.
}
\begin{center}
  {\LARGE\textbf{Equipment list}}
\end{center}
\begin{longtable}{|c|c|c|}
  \hline
  \textbf{ID}&\textbf{Equipment}&\textbf{Location}\\\hline
  \multicolumn{3}{|c|}{\textbf{Laser table facing computer or the wall} west $\rightarrow$ south}\\\hline
  1&Benchtop power 2chn for Cs MOT beat lock&Lv1 above 1.0 Cs MOT\\\hline
  2&PLL for Cs MOT&Below Cs MOT\\\hline
  3&Home power ($\pm$15,5)&Lv2 above Cs MOT\\\hline
  4&Valan&1.5 amplifier stack Lv1 above 1.0 Cs MOT\\\hline
  5&Till driver v2 for 1.5 Na Raman&Lv1 above 1.5 Na Raman\\\hline
  6&Temp servo for 1.5 Na Raman seed&Lv1 above 1.5 Na Raman\\\hline
  7&Temp servo for 1.5 Na Raman doubler&Lv1 above 1.5 Na Raman\\\hline
  8&PLL for Cs Raman&Next to 1.0 Cs Raman\\\hline
  9&New Focus driver x2 for Cs Raman&Lv1 above 1.0 Cs Raman\\\hline
  10&Benchtop power (x3)&Lv2 above 1.0 Cs MOT\\\hline
  11&Home power (24V) x2&Lv2 above 1.0 Cs Raman\\\hline
  12&Benchtop power&Lv1 next to New Focus drivers\\\hline
  13&Shutter driver&Lv1 above 1.0 Cs Raman\\\hline
  14&New Focus lock box for 1.0 Cs Raman&Lv1 above 1.0 Cs Raman\\\hline
  15&Thorlabs temp servo for 1.0 Na Raman doubler&Lv1 above 1.0 Na seed\\\hline
  16&Timebase drivers for 1.0 Na Raman and Na D2&Lv1 above Thorlabs temp servo\\\hline
  17&Benchtop power for 1.0 Cs Raman&Lv2 above New Focus lock box\\\hline
  18&High voltage power&Lv2 above timebase drivers\\\hline
  19&Home lock box for Na D2&Lv1 above 1.0 Na seed\\\hline
  20&MPB Raman laser&Lv1 above 1.0 Na MOT\\\hline
  21&Oscilloscope for Na D2 lock&Lv1 above MPB Raman laser\\\hline
  22&Benchtop power for 1.0 Na Raman seed&Lv2 above oscilloscope\\\hline
\end{longtable}
\twocolumn

\subsection{Equipments}
\DevDef{PLL for Cs MOT [2]}{
  \textbf{Below Cs MOT}\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug all signals (zip tie together)
  \item\OffBox Unplug 15V and 5V powers (zip tie together)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plugin 15V and 5V powers
  \item\OnBox Plugin all signals
  \item\OnBox Apply settings
  \end{itemize}
}
\DevDef{Valan [4]}{
  \textbf{1.5 amplifier stack Lv1 above 1.0 Cs MOT}\\
  Check with 1.5 to record setting\\

  \begin{tabular}{|c|c|}
    \hline
    Frequency&\hphantom{\hspace{3.5cm}}\\\hline
    Amplitude&\hphantom{\hspace{3.5cm}}\\\hline
  \end{tabular}\\

  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Restore settings
  \end{itemize}
}
\DevDef{Till driver v2 for 1.5 Na Raman [5]}{
  \textbf{Lv1 above 1.5 Na Raman}\\
  Record current values:\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power (zip tie to controller)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox Turn on
  \end{itemize}
}
\DevDef{Temp servo for 1.5 Na Raman seed [6]}{
  \textbf{Lv1 above 1.5 Na Raman}\\
  Check plugged into UPS.
}
\DevDef{Temp servo for 1.5 Na Raman doubler [7]}{
  \textbf{Lv1 above 1.5 Na Raman}\\
  Check plugged into UPS.
}
\DevDef{PLL for Cs Raman [8]}{
  \textbf{Next to 1.0 Cs Raman}\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug all signals (zip tie together)
  \item\OffBox Unplug 15V and 5V powers (zip tie together)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plugin 15V and 5V powers
  \item\OnBox Plugin all signals
  \item\OnBox Apply settings
  \end{itemize}
}
\DevDef{New Focus driver x2 for Cs Raman [9]}{
  \textbf{Lv1 above 1.0 Cs Raman}\\
  Record Temperature, Current, Piezo voltage\\
  Temperature is accessible in the menu under system status\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off output.
  \item\OffBox Check plugged into UPS.
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox (Turn on)
  \end{itemize}
}
\DevDef{Shutter driver [13]}{
  \textbf{Lv1 above 1.0 Cs Raman}\\
  Switch off/on with the switch on the back.
}
\DevDef{New Focus lock box for 1.0 Cs Raman [14]}{
  \textbf{Lv1 above 1.0 Cs Raman}\\
  Unplug power.
}
\DevDef{Thorlabs temp servo for 1.0 Na Raman doubler [15]}{
  \textbf{Lv1 above 1.0 Na seed}\\
  Record temperature settings\\

@@

  Check plugged into UPS.
}

\DevDef{Timebase drivers for 1.0 Na Raman and Na D2 [16]}{
  \textbf{Lv1 above Thorlabs temp servo}\\
  Record current and T1 settings\\

  \begin{tabular}{|c|c|}
    \hline
    Raman Current&\hphantom{\hspace{3.5cm}}\\\hline
    Raman T1&\\\hline
    D2 Current&\hphantom{\hspace{3.5cm}}\\\hline
    D2 T1&\\\hline
  \end{tabular}\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off output.
  \item\OffBox Check plugged into UPS.
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Turn on
  \end{itemize}
}

\DevDef{Home lock box for Na D2 [19]}{
  \textbf{Lv1 above 1.0 Na seed}\\
  \textbf{Turn on-off together with the adjustable high voltage power supply above}\\
  Record high voltage power supply output

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unlock
  \item\OffBox Turn down the voltage of the high voltage power supply to 0
  \item\OffBox Unplug high voltage power on lockbox (zip tie)
  \item\OffBox Unplug 15V from lockbox (zip tie)
  \item\OffBox Turn off high voltage power supply
  \item\OffBox Unplug high voltage power supply from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug high voltage power supply into the wall
  \item\OnBox Turn on high voltage power supply (make sure the output is 0)
  \item\OnBox Plug in 15V to lockbox
  \item\OnBox Plug in high voltage to lockbox
  \item\OnBox Turn up the voltage of the high voltage power supply
  \item\OnBox Check HV output
  \end{itemize}
}

\DevDef{MPB Raman laser [20]}{
  \textbf{Lv1 above 1.0 Na MOT}\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Power off
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into wall
  \item\OnBox Power on
  \end{itemize}
}
\DevDef{Oscilloscope for Na D2 lock [21]}{
  \textbf{Lv1 above MPB Raman laser}\\

  \begin{itemize}
  \item\OffBox Unplug from wall
  \end{itemize}
}
\subsection{Power supplies}
\DevDef{Benchtop power 2chn for Cs MOT beat lock [1]}{
  \textbf{Lv1 above 1.0 Cs MOT}\\
  Record voltage/current values:\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}

\DevDef{Home power ($\pm$15,5) [3]}{
  \textbf{Lv2 above Cs MOT}\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug load
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Switch off on the back
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Switch on
  \item\OnBox Plug the load back in
  \end{itemize}
}

\DevDef{Benchtop power (x3) [10]}{
  \textbf{Lv2 above 1.0 Cs MOT}\\
  Record voltage/current values:\\

  \begin{tabular}{|c|c|}
    \hline
    No. 1 Voltage&\hphantom{\hspace{3.5cm}}\\\hline
    No. 1 Current&\\\hline
    No. 2 Voltage&\\\hline
    No. 2 Current&\\\hline
    No. 3 Voltage&\\\hline
    No. 3 Current&\\\hline
  \end{tabular}\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}

\DevDef{Home power (24V) x2 [11]}{
  \textbf{Lv2 above 1.0 Cs Raman}\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug load
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Switch off on the back
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Switch on
  \item\OnBox Plug the load back in
  \end{itemize}
}

\DevDef{Benchtop power [12]}{
  \textbf{Lv1 next to New Focus driver}\\
  Record voltage/current values:\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}

\DevDef{Benchtop power for 1.0 Cs Raman [17]}{
  \textbf{Lv2 above New Focus lock box}\\
  Record voltage/current values:\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}

\DevDef{High voltage power [18]}{
  \textbf{Lv2 above timebase drivers}\\
  Follow home lock box for Na D2 [19].
}

\DevDef{Benchtop power for 1.0 Na Raman seed [22]}{
  \textbf{Lv2 above oscilloscope}\\
  Record voltage/current values:\\

  Check plugged into UPS.
}
\subsection{Computers}
\DevDef{Control computers}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Check update.
  \item\OffBox Turn off.
  \item\OffBox Unplug from UPS.
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Get UPS back
  \item\OnBox Turn on.
  \end{itemize}
}
\DevDef{Computer UPS}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Move to the lab.
  \item\OffBox Plug into backup power.
  \item\OffBox Plug in pump/temp controllers.
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug load back into the wall (or where they belongs).
  \item\OnBox Move back.
  \item\OnBox Plug computers back in.
  \end{itemize}
}

\onecolumn
\Person{Kenneth}{
  Equipments and power supplies are mostly located between the machine table and the laser table.
}
\begin{center}
  {\LARGE\textbf{Equipment list}}
\end{center}
\begin{longtable}{|c|c|c|}
  \hline
  \textbf{ID}&\textbf{Equipment}&\textbf{Location}\\\hline
  \multicolumn{3}{|c|}{\textbf{Laser table side facing machine table} north $\rightarrow$ east}\\\hline
  1&671 EOM stack&Floor\\\hline
  2&1550 Amp&Floor\\\hline
  3&Radio computer&Lv2\\\hline
  4&Benchtop power 2chn&Lv2 next to radio computer\\\hline
  5&High voltage power&Lv2 next to benchtop power\\\hline
  6&Variac for Na cell&Lv1 above 1.0 Na MOT\\\hline
  7&Shutter driver&Lv1 next to variac\\\hline
  8&Home lock box for 1.0 Na D1&Lv1 next to shutter driver\\\hline
  9&1038 Amp&Floor\\\hline
  10&1038 Timebase laser&Table\\\hline
  11&FPGA box for 1.0&Lv2\\\hline
  12&Thorlabs temp servo for Na D1 doubler&Lv1 above Na D1\\\hline
  13&Thorlabs temp servo for Na D1 seed&Lv1 above Na D1\\\hline
  14&Thorlabs current for Na D1 seed&Lv1 above Na D1\\\hline
  15&Benchtop power 2chn&Lv2 above Thorlabs controllers for Na D1 seed\\\hline
  16&Home power (24)&Lv2 next to benchtop power\\\hline
  17&Benchtop power x2 (2chn x1)&Lv2 next to Home power (24)\\\hline
  18&Till driver v2 for 976&Lv1 above Na D1 doubler\\\hline
  19&Thorlabs temp servo for Cs tweezer&Lv1 above Timebase 1038 beam\\\hline
  20&Thorlabs current (2A) (off)&Lv1 above Thorlabs temp servo\\\hline
  21&Till driver v2 for 671&Lv1 above Thorlabs current\\\hline
  22&Temp servo x2&Lv1 above Timebase 1038 control box\\\hline
  23&Oscilloscope&Lv1\\\hline
  \multicolumn{3}{|c|}{\textbf{Machine table side facing laser table} south}\\\hline
  24&Thorlabs current for 1.5 Cs MOT&Lv1 above 1.5 Cs\\\hline
  25&Till driver v2 for 1.5 Cs RP&Lv1 above 1.5 Cs\\\hline
  26&Temp servo (x2) for 1.5 Cs MOT/RP&Lv1 above 1.5 Cs\\\hline
  27&Oscilloscope for 1.5 Cs&Lv1 above 1.5 Cs\\\hline
  28&Home lock box for 1.5 Cs&Lv1 above 1.5 Cs\\\hline
  29&Novatec for 1.5 Cs lock&Lv1 above 1.5 Cs\\\hline
  30&Benchtop power 2chn&Lv2 1.5 Cs MOT/RP current\\\hline
  31&Home power (24) x2&Lv2 next to benchtop power\\\hline
  32&Benchtop power&Lv2 on two home power (24)\\\hline
  33&Home power ($\pm$15,5)&Lv2 middle\\\hline
  34&Benchtop power (x2) for uWave Amp&Lv2 next to home power ($\pm$15,5)\\\hline
  35&Benchtop power (x2)&Lv1 above 1.5 Na\\\hline
  36&High voltage power&Lv1 next to 2 benchtop power\\\hline
  37&Function generator for 1.0 MOT piezo&Lv1\\\hline
  38&Temperature and pump controllers for cavity&Lv1 next to function generator\\\hline
  39&Water chiller for uWave breadboard&Floor\\\hline
  40&SAES pump&Lv1 above 1.0 chamber\\\hline
  41&Benchtop power x2 (2chn x1)&Lv2 next to coil servo\\\hline
\end{longtable}
\twocolumn
\subsection{Equipments}
\DevDef{671 EOM stack [1]}{
  \textbf{Floor}\\
  Record voltage/current values:\\

  \begin{tabular}{|c|c|}
    \hline
    No. 1 Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
    No. 1 Left Current&\\\hline
    No. 1 Right Voltage&\\\hline
    No. 1 Right Current&\\\hline
    Thorlabs Current&\\\hline
    No. 2 Voltage&\\\hline
    No. 2 Current&\\\hline
    &\\\hline
    &\\\hline
    &\\\hline
  \end{tabular}\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \item\OffBox
  \item\OffBox
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \item\OnBox
  \item\OnBox
  \end{itemize}
}

\DevDef{1550 Amp [2]}{
  \textbf{Floor}\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox
  \item\OffBox
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox
  \item\OnBox
  \end{itemize}
}

\DevDef{Variac for Na cell [6]}{
  \textbf{Lv1 above 1.0 Na MOT}\\
  Record temperature and voltage settings\\

@@

  Check if we can use the backup power. (Through the UPS)
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn voltage to 0
  \item\OffBox Switch off
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into wall
  \item\OnBox Switch on
  \item\OnBox Turn the voltage up \textbf{SLOWLY} and monitor the temperature at the same time.
  \end{itemize}
}

\DevDef{Shutter driver [7]}{
  \textbf{Lv1 next to variac}\\
  Switch off/on with the switch on the back.
}

\DevDef{Home lock box for 1.0 Na D1 [8]}{
  \textbf{Lv1 next to shutter driver}\\
  \textbf{Turn on-off together with the fixed high voltage power supply above}\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unlock
  \item\OffBox Unplug high voltage power on lockbox (zip tie)
  \item\OffBox Unplug 15V from lockbox (zip tie)
  \item\OffBox Unplug high voltage power supply from walls
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug high voltage power supply into the wall
  \item\OnBox Plug in 15V to lockbox
  \item\OnBox Plug in high voltage to lockbox
  \item\OnBox Check HV output
  \end{itemize}
}

\DevDef{1038 Amp [9]}{
  \textbf{Floor}\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox
  \item\OffBox
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox
  \item\OnBox
  \end{itemize}
}

\DevDef{1038 Timebase laser [10]}{
  \textbf{Table}\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox
  \item\OffBox
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox
  \item\OnBox
  \end{itemize}
}

\DevDef{Thorlabs temp servo for Na D1 doubler [12]}{
  \textbf{Lv1 above Na D1}\\
  Record temperature settings\\

@@

  Check plugged into UPS.
}

\DevDef{Thorlabs temp servo for Na D1 seed [13]}{
  \textbf{Lv1 above Na D1}\\
  Record temperature settings\\

@@

  Check plugged into UPS.
}

\DevDef{Thorlabs current for Na D1 seed [14]}{
  \textbf{Lv1 above Na D1}\\
  Record current settings\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox Check current setting
  \item\OnBox Turn on
  \end{itemize}
}

\DevDef{Till driver v2 for 976 [18]}{
  \textbf{Lv1 above Na D1 doubler}\\
  Record current values:\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power (zip tie to controller)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox Turn on
  \end{itemize}
}

\DevDef{Thorlabs temp servo for Cs tweezer [19]}{
  \textbf{Lv1 above Timebase 1038 beam}\\
  Record temperature settings\\

  Check plugged into UPS.
}

\DevDef{Till driver v2 for 671 [21]}{
  \textbf{Lv1 above Thorlabs current}\\
  Record current values:\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power (zip tie to controller)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox Turn on
  \end{itemize}
}

\DevDef{Temp servo x2 [22]}{
  \textbf{Lv1 above Timebase 1038 control box}\\
  Check plugged into UPS.
}

\DevDef{Oscilloscope [23]}{
  \textbf{Lv1}\\

  \begin{itemize}
  \item\OffBox Unplug from wall
  \end{itemize}
}

\DevDef{Thorlabs current for 1.5 Cs MOT [24]}{
  \textbf{Lv1 above 1.5 Cs}\\
  Record current settings\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox Check current setting
  \item\OnBox Turn on
  \end{itemize}
}

\DevDef{Till driver v2 for 1.5 Cs RP [25]}{
  \textbf{Lv1 above 1.5 Cs}\\
  Record current values:\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power (zip tie to controller)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox Turn on
  \end{itemize}
}

\DevDef{Temp servo (x2) for 1.5 Cs MOT/RP [26]}{
  \textbf{Lv1 above 1.5 Cs}\\
  Check plugged into UPS.
}

\DevDef{Oscilloscope for 1.5 Cs [27]}{
  \textbf{Lv1 above 1.5 Cs}\\

  \begin{itemize}
  \item\OffBox Unplug from wall
  \end{itemize}
}

\DevDef{Home lock box for 1.5 Cs [28]}{
  \textbf{Lv1 above 1.5 Cs}\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unlock
  \item\OffBox Unplug 15V from lockbox (zip tie)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in 15V to lockbox
  \end{itemize}
}

\DevDef{Novatec for 1.5 Cs lock [29]}{
  \textbf{Lv1 above 1.5 Cs}\\

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Save settings
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Restore settings
  \end{itemize}
}

\DevDef{Function generator for 1.0 MOT piezo [37]}{
  \textbf{Lv1}\\

  \textbf{Turn on-off together with the HV amplifiers for 1.0 piezo mirrors above
    and the high voltage power supply on the left}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off the function generator
  \item\OffBox Unplug function generator output (zip tie and label)
  \item\OffBox Unplug HV power supply from the wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plugin HV power supply to the wall
  \item\OnBox Plugin function generator output
  \item\OnBox Turn on the function generator
  \end{itemize}
}

\DevDef{Temperature and pump controllers for cavity [38]}{
  \textbf{Lv1 next to function generator}\\

  Check plugged into UPS.
}

\DevDef{Water chiller for uWave breadboard [39]}{
  \textbf{Floor}\\
}

\DevDef{SAES pump [40]}{
  \textbf{Lv1 above 1.0 chamber}\\

  Check plugged into UPS.
}
\subsection{Power supplies}
\DevDef{Benchtop power 2chn [4]}{
  \textbf{Lv2 next to radio computer}\\
  Record voltage/current values:\\
